\begin{thebibliography}{99}
\addcontentsline{toc}{section}{参考文献}

\bibitem{radford2021learning} Radford A, Kim J W, Hallacy C, et al. Learning Transferable Visual Models From Natural Language Supervision[C]. Proceedings of the 38th International Conference on Machine Learning (ICML), 2021: 8748-8763.

\bibitem{hu2022lora} Hu E J, Shen Y, Wallis P, et al. LoRA: Low-Rank Adaptation of Large Language Models[C]. International Conference on Learning Representations (ICLR), 2022.

\bibitem{li2023blip2} Li J, Li D, Savarese S, et al. BLIP-2: Bootstrapping Language-Image Pre-training with Frozen Image Encoders and Large Language Models[C]. International Conference on Machine Learning (ICML), 2023.

\bibitem{liu2024llava} Liu H, Li C, Wu Q, et al. Visual Instruction Tuning[C]. Advances in Neural Information Processing Systems (NeurIPS), 2023.

\bibitem{bai2023qwen} Bai J, Bai S, Yang S, et al. Qwen-VL: A Versatile Vision-Language Model for Understanding, Localization, Text Reading, and Beyond[J]. arXiv preprint arXiv:2308.12966, 2023.

\bibitem{zhai2023sigmoid} Zhai X, Mustafa B, Kolesnikov A, et al. Sigmoid Loss for Language Image Pre-Training[C]. Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV), 2023: 41-50.

\bibitem{spampinato2017deep} Spampinato C, Palazzo S, Kavasidis I, et al. Deep Learning Human Mind for Automated Visual Classification[C]. Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2017: 6809-6817.

\bibitem{palazzo2017decoding} Palazzo S, Spampinato C, Kavasidis I, et al. Decoding Brain Representations by Multimodal Learning of Neural Activity and Visual Features[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 2017, 43(11): 3833-3849.

\bibitem{tirupattur2018thoughtviz} Tirupattur P, Rawat Y S, Spampinato C, et al. ThoughtViz: Visualizing Human Thoughts Using Generative Adversarial Network[C]. Proceedings of the 26th ACM International Conference on Multimedia, 2018: 950-958.

\bibitem{kavasidis2017spatio} Kavasidis I, Palazzo S, Spampinato C, et al. Brain2Image: Converting Brain Signals into Images[C]. Proceedings of the 25th ACM International Conference on Multimedia, 2017: 1809-1817.

\bibitem{gifford2023alanet} Gifford A T, Lahner B, Saba-Sadiya S, et al. The Algonauts Project 2023 Challenge: How the Human Brain Makes Sense of Natural Scenes[J]. arXiv preprint arXiv:2301.03198, 2023.

\bibitem{hebron2024things} Hebron H, Luo X, Bonnen T, et al. THINGS-EEG2: A Large-Scale Neuroimaging Dataset of Human Brain Responses to Natural Images[J]. bioRxiv, 2024.

\bibitem{du2023eegclip} Du C, Fu K, Li J, et al. Decoding Visual Neural Representations by Multimodal Learning of Brain-Visual-Linguistic Features[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 2023, 45(9): 10760-10777.

\bibitem{devlin2019bert} Devlin J, Chang M W, Lee K, et al. BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding[C]. Proceedings of NAACL-HLT, 2019: 4171-4186.

\bibitem{dosovitskiy2021vit} Dosovitskiy A, Beyer L, Kolesnikov A, et al. An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale[C]. International Conference on Learning Representations (ICLR), 2021.

\bibitem{vaswani2017attention} Vaswani A, Shazeer N, Parmar N, et al. Attention Is All You Need[C]. Advances in Neural Information Processing Systems (NeurIPS), 2017: 5998-6008.

\bibitem{touvron2023llama} Touvron H, Martin L, Stone K, et al. Llama 2: Open Foundation and Fine-Tuned Chat Models[J]. arXiv preprint arXiv:2307.09288, 2023.

\bibitem{schrimpf2018brain} Schrimpf M, Kubilius J, Hong H, et al. Brain-Score: Which Artificial Neural Network for Object Recognition is most Brain-Like?[J]. bioRxiv, 2018: 407007.

\bibitem{cichy2016comparison} Cichy R M, Pantazis D, Oliva A. Similarity-Based Fusion of MEG and fMRI Reveals Spatio-Temporal Dynamics in Human Cortex During Visual Object Recognition[J]. Cerebral Cortex, 2016, 26(8): 3563-3579.

\bibitem{chen2023shikra} Chen K, Zhang Z, Zeng W, et al. Shikra: Unleashing Multimodal LLM's Referential Dialogue Magic[J]. arXiv preprint arXiv:2306.15195, 2023.

\bibitem{ho2020denoising} Ho J, Jain A, Abbeel P. Denoising Diffusion Probabilistic Models[C]. Advances in Neural Information Processing Systems (NeurIPS), 2020: 6840-6851.

\bibitem{rombach2022high} Rombach R, Blattmann A, Lorenz D, et al. High-Resolution Image Synthesis with Latent Diffusion Models[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), 2022: 10684-10695.

\bibitem{wang2022imagenet} Wang J, Liu Z, Li S, et al. A Survey of Recent Advances in EEG-based Visual Decoding and Image Reconstruction[J]. Frontiers in Neuroscience, 2022, 16: 851754.

\end{thebibliography}
